Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-03 prop.tex
prop.tex \section{Quantum Interval-valued Probability Measures} Updating

\noindent It is easy to establish that quantum interval-valued probability
measures generalize conventional quantum probability measures. In
particular, any quantum probability measure can be recast as an interval-valued
measure using the three intervals $\left[0,0\right]$, $\left[1,1\right]$
and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$ and $\left[1,1\right]$
are called \imposs~and \necess~as before, and \emph{$\left[0,1\right]$}
is called \unknown~because it provides no information. Given a quantum
probability measure~$\mu:\events\rightarrow\left[0,1\right]$, we
define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is defined by 
\begin{equation}
\iota(x)=\begin{cases}
\necess & \textrm{if }x=1\textrm{ ;}\\
\imposs & \textrm{if }x=0\textrm{ ;}\\
\unknown & \textrm{otherwise.}
\end{cases}\label{eq:homomorphism}
\end{equation}
This measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question. Formally,
we can ask: what can we deduce about the state of a quantum system
given a quantum interval-valued probability measure, i.e., given observations
done with finite resources. In the case the intervals are infinitely
precise the question reduces to Gleason's theorem which states that
the state of the quantum system is uniquely determined by the probability
measure. But surely the less resources are available, the less precise
the intervals, and the less we expect to know about the state of the
system. To formally state and answer this question we begin with defining
the \emph{core} and \emph{convexity} of a probability measure as follows.

@@

>>>>

\noindent It is easy to establish that quantum interval-valued probability
measures generalize conventional quantum probability measures. In
particular, any quantum probability measure can be recast as an interval-valued
measure using the three intervals $\left[0,0\right]$, $\left[1,1\right]$
and \emph{$\left[0,1\right]$}, where $\left[0,0\right]$ and $\left[1,1\right]$
are called \imposs~and \necess~as before, and \emph{$\left[0,1\right]$}
is called \unknown~because it provides no information. Given a quantum
probability measure~$\mu:\events\rightarrow\left[0,1\right]$, we
define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is defined by 
\begin{equation}
\iota(x)=\begin{cases}
\necess & \textrm{if }x=1\textrm{ ;}\\
\imposs & \textrm{if }x=0\textrm{ ;}\\
\unknown & \textrm{otherwise.}
\end{cases}\label{eq:homomorphism}
\end{equation}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{measure3} 
\par\end{centering}
\caption{\label{fig:three-dimensional-3-value}This figure illustrates the
1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{B}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
plotted in $\mathbb{R}^{3}$. The red vector is $\ket{0}$, and $\bar{\mu}_{\ket{0}}^{B}\left(\proj{0}\right)=\necess$.
$\ket{0}$ is the normal vector of the plane so that for any vector~$\ket{\psi}$
in the plane, we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\imposs$.
For any other vector~$\ket{\psi}$, we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\unknown$.}
\end{figure}
For example, Fig.~\ref{fig:three-dimensional-3-value} plots the
1-dimensional projectors mapped by $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$.
This measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question. Formally,
we can ask: what can we deduce about the state of a quantum system
given a quantum interval-valued probability measure, i.e., given observations
done with finite resources. In the case the intervals are infinitely
precise the question reduces to Gleason's theorem which states that
the state of the quantum system is uniquely determined by the probability
measure. But surely the less resources are available, the less precise
the intervals, and the less we expect to know about the state of the
system. To formally state and answer this question we begin with defining
the \emph{core} and \emph{convexity} of a probability measure as follows.

@@

In general, each two 1-dimensional projectors~$\proj{\psi_{0}}$
and $\proj{\psi_{1}}$ mapping to $\imposs$ suggests $\bar{\mu}$
might be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$
in the Hilbert space of dimension 3. As we illustrated in figure~\ref{fig:three-dimensional-3-value},
if $\bar{\mu}$ has a non-empty core, the states mapping to $\imposs$
is contained a plane, which contains no area in the sphere.
